quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-01 paper-quollr.Rmd
Updated polygon_ID description

For each centroid, six vertices are computed and assigned a polygon ID (`h`) corresponding to the centroid’s `h`. These points are aggregated into a tibble that includes the polygon ID (`h`) and the respective x (`x`) and y (`y`) coordinates for all hexagon corners.

>>>>

For each centroid, six vertices are computed and assigned a polygon ID as the centroid. These vertices are then combined into a tibble that records the polygon ID (`h`) and the respective x (`x`) and y (`y`) coordinates for all hexagon corners.
